Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-06-25 analysis2_manuscript.tex
Further description of sweeps for ref 1

    % sweep interface
    While the \texttt{DFE} class facilitates the simulation of non-neutral variation across a sequence,
    it does not provide a means of specifying the origin and fate of particular selected alleles.
    Thus, we have also implemented an API in \stdpopsim (\texttt{stdpopsim.selective\_sweep}) that enables 
    selective sweeps to be simulated with a high degree of control.
    This function augments a demographic model by introducing an advantageous mutation over a given time interval,
    at a given position along the sequence; and conditions the simulation such that the mutation is above a particular 
    frequency at the beginning and end of the sweep period.
    As this functionality is implemented on top of the existing \stdpopsim API, it may be combined with other 
    models of selection and demography to simulate the combined effects of multiple, disparate evolutionary processes
    on genetic variation in a population.

@@

>>>>

    % sweep interface
    While the \texttt{DFE} class facilitates the simulation of non-neutral variation across a sequence,
    it does not provide a means of specifying the origin and fate of particular selected alleles.
    Thus, we have also implemented an API in \stdpopsim (\texttt{stdpopsim.selective\_sweep}) that enables 
    selective sweeps to be simulated with a high degree of control.
    This function augments a demographic model by introducing an advantageous mutation over a given time interval,
    at a given position along the sequence; and conditions the simulation such that the mutation is above a particular 
    frequency at the beginning and end of the sweep period.
    The conditioning is implemented via rejection sampling; if the frequency of the advantageous allele 
    drifts out of the prescribed bounds, the simulation is restarted from the introduction of 
    the advantageous allele. If there are competing advantageous alleles (e.g. simultaneous sweeps at distinct loci) 
    then the simulation is restarted from the introduction of the first of these.
    As this functionality is implemented on top of the existing \stdpopsim API, it may be combined with other 
    models of selection and demography to simulate the combined effects of multiple, disparate evolutionary processes
    on genetic variation in a population.

@@

    % NSP: added to address reviewer 1's comments asking for more detail. Not adding
    % any detail regarding the lower-level interface (particular "extended events") as
    % these may change.
    \subsection*{Selective sweeps and rejection sampling}

    Selective sweeps are implemented in the \slim engine by
    introducing a mutation with a fitness effect of $h s$ where $h$ is the
    dominance coefficient (as for the DFE model) and $s \geq 0$ is the
    selection coefficient.  The allele is introduced in a given population at
    a specified time and genomic position, and may be either globally or locally
    adaptive (so that the fitness effect is confined to the population of
    origin) over a fixed duration. To model sweeps from standing genetic
    variation (so-called ``soft sweeps''), the allele may be introduced at a
    given frequency, in which case carriers are selected at random at the
    initiation of the sweep.

    Crucially, the advantageous allele must remain extant over the course of
    the sweep; this conditioning is accomplished via rejection sampling,
    whereby the simulation is restarted from the onset of the sweep if the
    allele drifts out of the population of origin (or alternatively, below a
    user-specified frequency). If there are competing advantageous alleles
    (simultaneous sweeps at distinct loci) and one of these drifts out of
    bounds, then the simulation is restarted from the onset of the first sweep;
    this avoids conditioning on particular (partial) allele frequency
    trajectories for the remaining alleles.  A downside of this strategy is
    that rejection becomes more likely with increasing numbers of simultaneous
    sweeps or with hard-to-satisfy constraints; but it allows for greater
    flexibility in sweep specification and for interoperability with the
    \stdpopsim DFE model.
